\section{Evaluation of Assignment}
We have had a lot of fun during this exercise. Playing around with different sounds and using a DAC to generate sound has been quite rewarding. There are however some opinions about this exercise that we would like to present. The first one being a lack of hints in the compendium. Energy efficiency conserned, we felt that we should have been provided with more hints than the sentence: \emph{You can generate sound even with busy-waiting in a loop and writing to the DAC afterwards, but this will be very energy-inecient}\\
\\
The compendium informed about using the DMA, but was clear in it's warnings against using it. Also, we observed that many of the groups, us included, used some kind of tools other than the C language. The tools where primarly used for converting from a sound format to a format the application understands. We created a python script that generated C code from a spread sheet. This became an important part of the system we developed. We feel that the assignment description should contain some tips telling the reader to use a script for the more repetitive part of the assignment.\\
\\
This assignment was as much about sound waves as programming the development board. Even though the physics around sound waves is an interesting subject, we do not think it relates to what this course is about. Perhaps focusing more on energy efficiency and less on sound waves could improve this assignment. \\
\\
However, we are happy with the assignment. Both the learning outcome and the fun we had in the development process has without any doubt been satisfactory.
