\section{Results and Tests}

\subsection{Testing functionality}
We tested that our application worked as it should by observing how the system reacted to button press on the gamepad. The buttons have the following defined behaviour:
\begin{itemize}
	\item \emph{Button 1} - 
	\item \emph{Button 2} - Change to sawtooth waveform.
	\item \emph{Button 3} - Change to triangle waveform.
	\item \emph{Button 4} - Change to square waveform.
	\item \emph{Button 5} - Play Tetris Theme Song, our startup melody.
	\item \emph{Button 6} - Play Star Wars Imperial March.
	\item \emph{Button 7} - Play sound effect 1.
	\item \emph{Button 8} - Play sound effect 2.
\end{itemize}

We could indeed confirm that buttons 5-8 played the auido we expected. \\
\\
When we tested the different waveforms (button 2, 3 and 4), none of us had any idea what the different waves would sound like. We observed that the audio indeed sounded differently (more or less metallic), but still correct (as described in \ref{audio_correctness}). We therefore concluded that waveform selection functionality was working properly.

\subsubsection{Audio correctness and quality}
\label{audio_correctness}
We have no knowledge of how to scientifically test the audio correctness and quality, so we used our own ears. We accepted the music and sound effects if they "sounded allright". By that we mean that all the tones in the audio was pure, playing in the correct tempo and having the expected pitch. 

\subsection{Testing energy efficiency}
Gå igjennom høyfrekvent, lavfrekvent og sovning etter ferdig avspilling.
